\documentclass[11 pt]{article}
\usepackage[a4paper, total={6in, 8in}]{geometry}
\usepackage{float}
\usepackage{multirow}    % to add multirow cells in tables
\usepackage{indentfirst} %to automatically intent the first paragrap of each sections
\usepackage{amsmath}		%math packages
\usepackage{mathtools}
\usepackage{amssymb}
\usepackage{graphicx}	%Required for inserting images
\usepackage{fontenc}
\usepackage{hyperref}	%for hyperlinks
\usepackage{subcaption}	%to add subcaptions within single floating enviroments
\usepackage{placeins}	%to control position of floating enviroments
\title{F61: Nuclear Magnetic Resonance}
\author{Paris J. Huth \& Q'inich Figueroa}
\date{May 2024}

\begin{document}
\maketitle
\begin{center}
\begin{abstract}
In the experiment we study properties and usages of nuclear magnetic resonance (NMR). Firstly we measured the characteristic relaxation times $T_1$ and $T_2$ of two probes. The later of which was estimated with the Hahn echo and Carr-Purcell sequence. The results of which were then compared. Secondly NMR was used to identify substances using  the characteristic chemical shift with TMS (Tetramethylsilane $\mathrm{Si}\left(\mathrm{CH_3}\right)_4$) as reference substance. Lastly NRM was used for 1 dimensional and 2 dimensional imaging.  
\end{abstract}
\end{center}

\input{F61_Basics}
\input{F61_Measurements}
\input{F61_Results}
\newpage
\section{Critical Discussion}
%resumé of experiment.
The goal of the experiment was to study and get familiar with the theory and implementations of nuclear magnetic resonance. For that we studied two methods to measure the spin-spin relaxation time and one to estimate the spin-lattice relaxation time.


% -> mention problems minimizing the signal for the 180° pulse
	%-> maybe the problems with the measurements of T_1 originate from the 180° 
	%	which could not be set to 0.
	
We examined two samples, Gd500 (1 part Gd to 5 parts water) and Gd600 (1 part Gd to 6 parts water), for which we obtained $T_1$ times using 180°-90° sequences: $T_{1,500} = 159.0 ± 1.3 \text{ ms}$ and $T_{1,600} = 154.4 ± 1.2 \text{ ms}$. These times decrease with an decrease in gadolinium concentration. To be expected, was a decrease in potential to dissipate energy, with a higher degree of dilution and thus a faster $T_1$ time for higher concentration. This is the behavior we observe when taking the $T_2$ measurements. Both the spin-echo and Carr-Purcell values increased with a lower concentration. The spin-echo sequence yielded $T_{2,500} = 110 ± 6 \text{ ms}$ and $T_{2,600} = 115.7 ± 1.2 \text{ ms}$, and the Carr-Purcell sequence yielded $T_{2,500} = 111.3 ± 1.5 \text{ ms}$ and $T_{2,600} = 116.9 ± 0.9 \text{ ms}$.	
	
Repeated testing did not change the relationship of these values, leading us to the conclusion of a potential setup error, either in the NMR device itself or, more likely, the Gd500 or Gd600 samples.  We expect the results from the Carr-Purcell method to show a smaller deviation from the true value of $T_2$ for a given sample.



 Later we identified 5 probes by measuring the relative chemical shift, where we used TMS as reference substance.
 We inserted each of the 5 probes, with and without the reference substance, and took measurements while rotating them with compressed air. The process of rotating proved to be somewhat finicky, which is why some of the spectra include more noise than the others. Nevertheless, we were able to identify all the probes, starting with substance A, which had to be fluroacetone because of its 3 distinct peaks, which no other probe could produce. Probe D showed the active group $FH_2$, which was already present in fluroacetone and thus had to be fluoroacetonitril. The spectrum of the probes B and E showed identical chemical shifts, although the intensity of the maxima varied. The maxima of probe B have show an increased intensity compared to probe E due to the presents of two $CH_3$ groups compared to the one group contained in probe E. Thus probe B being p-xylol and E being toluol. Lastly, probe C corresponded to acetic acid due to its big chemical shift by the active group $COOH$.



  Next, we used NMR for imaging. In this last part we first got familiar with the operation by taking 1 dimensional scans. 
We examined different vials filled with oil and tested the extend of the viable measurement range. Values obtained outside the $x\in\left[-15mm, 15mm\right]$ range deviated in terms of intensity due to the non-linearity of the field gradient. This was obtained measuring two vials of oil of varying length. We also examined a vile containing a teflon probe. Since teflon does not produce a NMR signal, one could identify the structure of said probe by the lack of signal, caused by the displacement of oil.
  
Then we used 1 dimensional imaging to determine the nature of the time evolution of a system. A vial filled with sand was topped of with a few milliliters of oil and imaged over time. The measurements depict the movement and filtering of the fluid through the porous material, rather than a diffusion, since a concavity is clearly visible in the evolution of the system.

 
Finally we use 2D imaging to map different objects and its structures. Starting off with the capturing  of  oil, both horizontally and vertically, to ensure expected behavior of system. After confirming, we continued on to imaging a peanut, trying to reveal both nuts inside its shell using a vertical scan, also showing the air gap within a single nut, in both the horizontal and vertical slice.
It proved itself difficult setup the vertical and horizontal offset for imaging, and to choose the right slice thickness, to gain a satisfying result and signal strength, which is why we chose to continue with horizontal images. The scan of the pecan revealed the nut contained within its shell, and the celery showed its characteristic c-shape. One could also identify finer structures within the celery, due to its fitting setup and structure.
The attempts at imaging a chili did not provide any viable results, due to yielding too weak of a signal, or low discernibility at higher slice thickness.
%imaging 
% --> mention results
% --> difficulties? there were but can't really remember them


\end{document}
